### 2009-06-16 paper.tex
ranking of factors affecting accuracy

\paragraph{The Outside algorithm.}
The Outside algorithm is primarily used an an intermediary for posterior decoding on the model.  It is analogous to the Backward algorithm for HMMs.

@@

With the AMA statistic, as with the perfect alignment rate, the most important factor distinguishing the various models
is clearly the incorporation of some form of basepair structure:
structure-less \handel\  (regardless of linear {\em vs} affine gap penalty) performs much worse than the structure-aware SCFG methods.
Intuitively, this is to be expected: whenever a basepair-aware method aligns one half of a basepair, it gets the other nucleotide
correctly aligned for free.

>>>>

\paragraph{The Outside algorithm.}
The Outside algorithm is primarily used an an intermediary for calculating nucleotide-level posterior probabilities, e.g. for posterior decoding on the model.
It is analogous to the Backward algorithm for HMMs.

@@

Taken together, these results show that the most important factor distinguishing the various models
is the incorporation of some form of basepair structure:
structure-less \handel\  (regardless of linear {\em vs} affine gap penalty) performs much worse than the structure-aware SCFG methods.
Intuitively, this is to be expected: whenever a basepair-aware method aligns one half of a basepair, it gets the other nucleotide
correctly aligned for free.

The second most important, amongst the factors we have considered in this experiment, is use of the correct posterior-decoding algorithm for the objective function at hand
(c.f. \stemloc\ {\em vs} \stemlocama).
An obvious corollorary is the importance of choosing an appropriate objective function in the first place
(c.f. perfect alignment rate {\em vs} AMA).

Lastly, the fine details of the scoring scheme---including branch lengths, substitution scores, gap penalties and so forth---appear to
be the least important of the factors we considered, yielding observable differences only when all other aspects of the inference procedure were more-or-less equal.
